Optimizing DTW-Based Audio-to-MIDI Alignment and Matching

### 2015-09-17 paper.tex
Add outline

\cite{hu2003polyphonic}

>>>>

Why is MIDI to audio alignment important?  Matching?

Systems which do alignment

Systems which do matching \cite{hu2003polyphonic} plus KDD literature

\section{DTW-Based Alignment}

Formal definition of DTW-based alignment, with parameter and representation discussion

Discussion of extracting a confidence score, normalization methods

\section{Creating a Synthetic Alignment Dataset}

Collection of MIDI files

``Easy'' corruption, for alignment accuracy

``Hard'' corruption, for matching accuracy

\section{Optimizing DTW-Based Alignment}

Short overview of Bayesian optimization

Parameter space (including multiplicative penalty)

Random trials

Discussion of best-performing aligners; also best aligner with beats

\section{Optimizing Confidence Reporting}

Grid search

Statistical tests used

Choosing the best alignment scheme (with algorithm box?)

\section{Qualitative Evaluation}

Data preparation

Evaluation criteria

Results

\section{Avenues for Improvement}

Augmentation with MUDA, partial alignments, robustness to missing instruments, re-training specifically on subsequences
